---
title: "Salman Khan Shape Analysis"
output: html_notebook
---

This code turns the otolith images into wavelet shape co-efficients (can also fo fourier transformation)

This code is based on Libungan & Palsson 2015  https://doi.org/10.1371/journal.pone.0121102

This first one will skip most of the following code which is really slow (can only use if this file exists)
```{r}
load("../Data/Shape_outlines_smoothed.RData")
```


Start here if this is the first time.
```{r}
#install.packages("shapeR")
library(shapeR)
library(vegan)
```

Load images - this needs full directory address to work
```{r}
shape = shapeR("D:/Salman Khan India/MGLMs-Otoliths/ShapeAnalysis", "FISH.csv")
```

Outline Extraction

```{r}
shape = detect.outline(shape, threshold = 0.1, write.outline.w.org = TRUE)
```


Remove dud outlines and re-run with different threshold - this is a large amount of trial and error
```{r}
shape = remove.outline(shape, "AG", "001_1")
shape = remove.outline(shape, "AG", "001_5")
shape = remove.outline(shape, "AG", "001_10")
shape = remove.outline(shape, "AG", "001_12")
shape = remove.outline(shape, "AG", "001_13")
shape = remove.outline(shape, "AG", "001_14")
shape = remove.outline(shape, "AG", "001_15")
shape = remove.outline(shape, "AG", "001_16")


shape = remove.outline(shape, "LU", "002_6")
shape = remove.outline(shape, "LU", "002_7")
shape = remove.outline(shape, "LU", "002_11")
shape = remove.outline(shape, "LU", "002_13")
shape = remove.outline(shape, "LU", "002_17")


shape = remove.outline(shape, "NN", "003_3")
shape = remove.outline(shape, "NN", "003_7")
shape = remove.outline(shape, "NN", "003_9")
shape = remove.outline(shape, "NN", "003_10")
shape = remove.outline(shape, "NN", "003_11")
shape = remove.outline(shape, "NN", "003_12")
shape = remove.outline(shape, "NN", "003_13")
shape = remove.outline(shape, "NN", "003_15")
shape = remove.outline(shape, "NN", "003_17")
shape = remove.outline(shape, "NN", "003_18")

shape = detect.outline(shape, threshold = 0.2, write.outline.w.org = TRUE)
```

```{r}
shape = remove.outline(shape, "AG", "001_1")
shape = remove.outline(shape, "AG", "001_5")
shape = remove.outline(shape, "AG", "001_12")
shape = remove.outline(shape, "AG", "001_13")
shape = remove.outline(shape, "AG", "001_15")
shape = remove.outline(shape, "AG", "001_16")


shape = remove.outline(shape, "LU", "002_6")
shape = remove.outline(shape, "LU", "002_13")


shape = remove.outline(shape, "NN", "003_9")
shape = remove.outline(shape, "NN", "003_11")
shape = remove.outline(shape, "NN", "003_12")
shape = remove.outline(shape, "NN", "003_13")
shape = remove.outline(shape, "NN", "003_15")
shape = remove.outline(shape, "NN", "003_18")

shape = detect.outline(shape, threshold = 0.3, write.outline.w.org = TRUE)
```

Now edit in GIMP (image manipulation program) and do again
```{r}
shape = remove.outline(shape, "AG", "001_1")
shape = remove.outline(shape, "AG", "001_5")
shape = remove.outline(shape, "AG", "001_12")
shape = remove.outline(shape, "AG", "001_13")
shape = remove.outline(shape, "AG", "001_15")
shape = remove.outline(shape, "AG", "001_16")


shape = remove.outline(shape, "LU", "002_6")
shape = remove.outline(shape, "LU", "002_13")


shape = remove.outline(shape, "NN", "003_11")
shape = remove.outline(shape, "NN", "003_12")
shape = remove.outline(shape, "NN", "003_13")
shape = remove.outline(shape, "NN", "003_18")

shape = detect.outline(shape, threshold = 0.2, write.outline.w.org = TRUE)
```

```{r}
shape = remove.outline(shape, "AG", "001_1")
shape = remove.outline(shape, "AG", "001_5")
shape = remove.outline(shape, "AG", "001_12")
shape = remove.outline(shape, "AG", "001_13")
shape = remove.outline(shape, "AG", "001_15")
shape = remove.outline(shape, "AG", "001_16")


shape = remove.outline(shape, "LU", "002_6")
shape = remove.outline(shape, "LU", "002_13")


shape = remove.outline(shape, "NN", "003_3")
shape = remove.outline(shape, "NN", "003_16")

shape = detect.outline(shape, threshold = 0.15, write.outline.w.org = TRUE)
```

Fine touch the otoliths and re-run with the mouse.click in the console. Run this in the console, not a R notebook.
```{r}

shape = remove.outline(shape, "NN", "003_4")

# Run in console
#shape = detect.outline(shape, threshold = 0.3, write.outline.w.org = TRUE, mouse.click=TRUE)
```



```{r}
save(shape, file = "Shape_outlines.RData")
```



```{r}
shape = smoothout(shape, n=100)
```

```{r}
save(shape, file = "../Data/Shape_outlines_smoothed.RData")
```


Start from here if you loaded the smoothed data

```{r}
shape = generateShapeCoefficients(shape)
shape = enrich.master.list(shape)
```




```{r}
getMeasurements(shape)
tapply(getMeasurements(shape)$otolith.area, getMasterlist(shape)$pop, mean)
```



```{r}
plotWaveletShape(shape, "pop", show.angle = TRUE)
plotFourierShape(shape, "pop", show.angle = TRUE)
```


```{r}
shape = stdCoefs(shape, classes = 'pop', "length_cm", bonferroni = TRUE)
```

Find how good the estimation is - 10 Wavelets = 
```{r}
est.list = estimate.outline.reconstruction(shape)
p <- outline.reconstruction.plot(est.list, max.num.harmonics = 15)
p
```

```{r}
est.list$w.dev.m
```




```{r}
plotWavelet(shape, level = 5, class.name = "pop", useStdcoef = TRUE)
```



Classification Techniques

```{r}
cap.res = capscale(getStdWavelet(shape) ~ getMasterlist(shape)$pop)
anova.cca(cap.res, by = "terms", step = 1000)
shape.data <- getStdWavelet(shape)
shape.info <- getMasterlist(shape)
shape.combined.data <- cbind(shape.info, shape.data)

write.csv(shape.combined.data, file = "../Data/shape_data.csv", row.names = F)

```



